 

### 2020-10-01 vertical-thermal-review.Rmd
update

**Air temperature, $T_{air}$, is sometimes significantly buffered by forest canopies (Fig. **2x**).**
Studies comparing $T_{air}$ under forest canopies with nearby clearings have found lower maximum temperatures under forest canopies across Europe [@zellweger_seasonal_2019; @vonarxSpatiotemporalEffectsForest2012] and in the northwestern United States [@davis_microclimatic_2019]. 
Similarly, maximum air temperatures were higher above than below tropical forest canopies during wet seasons in Panama [@rey-sanchez_spatial_2016] and coastal Brazil [@fauset_differences_2018, Tymen et al. 2017]. 
"max temps were higher and humidity lower in gaps vs understory regions (both at 1.5 m above the ground), see Fig. 4 - again illustrating buffering effect of the canopy".
However, similar maximum temperatures have been observed during the dry season in Panama [@rey-sanchez_spatial_2016] and in a temperate deciduous forest in the eastern United States [@mcgregor_tree_nodate].
Minimum $T_{air}$ is also buffered by forest canopies under some conditions. 
Higher minimum temperatures under forest canopies relative to nearby clearings have been observed across Europe [@zellweger_seasonal_2019] and in the northwestern United States [@davis_microclimatic_2019].
However, similar minimum temperatures under forest canopies have been observed in tropical forests in Panama [@rey-sanchez_spatial_2016] and coastal Brazil [@fauset_differences_2018], as well as in a temperate deciduous forest in the eastern United States [@mcgregor_tree_nodate; @nakamuraForestsTheirCanopies2017].
*(Add something about risk of freeze.)*--> [@nakamuraForestsTheirCanopies2017]

>>>>

**Air temperature, $T_{air}$, is sometimes significantly buffered by forest canopies (Fig. **2x**).**
Studies comparing $T_{air}$ under forest canopies with nearby clearings have found lower maximum temperatures under forest canopies across Europe [@zellweger_seasonal_2019; @vonarxSpatiotemporalEffectsForest2012] and in the northwestern United States [@davis_microclimatic_2019]. 
Similarly, maximum air temperatures were higher above than below tropical forest canopies during wet seasons in Panama [@rey-sanchez_spatial_2016] and coastal Brazil [@fauset_differences_2018, Tymen et al. 2017]. 
"max temps were higher and humidity lower in gaps vs understory regions (both at 1.5 m above the ground), see Fig. 4 - again illustrating buffering effect of the canopy".
However, similar maximum temperatures have been observed during the dry season in Panama [@rey-sanchez_spatial_2016] and in a temperate deciduous forest in the eastern United States [@mcgregor_tree_nodate].
Minimum $T_{air}$ is also buffered by forest canopies under some conditions. 
Higher minimum temperatures under forest canopies relative to nearby clearings have been observed across Europe [@zellweger_seasonal_2019] and in the northwestern United States [@davis_microclimatic_2019].
However, similar minimum temperatures under forest canopies have been observed in tropical forests in Panama [@rey-sanchez_spatial_2016] and coastal Brazil [@fauset_differences_2018], as well as in a temperate deciduous forest in the eastern United States [@mcgregor_tree_nodate; @nakamuraForestsTheirCanopies2017].
*(Add something about risk of freeze.)* Additionally, canopies also buffer effects of snow through intercepting heavy snow accumulution on below-canopy levels [@nakamuraForestsTheirCanopies2017; @storckMeasurementSnowInterception2002]
